External Patch Group Prior Guided Internal Clustering and Subspace Learning for Real Image Denoising

### 2016-10-10 egpaper_for_review.tex
modf

\subsection{Our Contributions}
The contributions of this paper are summarized as follows:
\begin{itemize}
\item To avoid noise modeling and estimation, we propose a noval learning based model which directly transform noisy images into clean conuterparts;
\item To learn without paired training images, we perform the learning on paired image patches extracted from unpaired noisy and clean images;
\item To deal with different structures and nise sources, we employ a "divide-and-coquer" strategy on the training data, and for each paired cluster of similar patches, we learn two dictionaries and transformation function for noisy and clean data;
\item The proposed method achieves better performance than other competing methdos on real noisy image denoising problem.
\end{itemize}

\section{Related Work}
\subsection{Couple dictionary learning}
Coupled dictionary learning (CDL) is a frequently used learning framework for cross-style image synthesis problems, such as image super-resolution, photo-sketch synthesis. CDL aims at learning a pair of dictionaries as well as the relationships between the two cross-domain image styles. Hence, the information from the source image style can be applied to synthesize the image at the target style. The relationships are often assumed to be identical mapping (coupled) \cite{yang2010image}, linear mapping (semi-coupled) \cite{wang2012semi}. Yang et al. \cite{yang2010image} assumed that LR image patches have the same sparse representations as their HR versions do, and proposed a joint dictionary learning model for SR using concatenated HR/LR image features. They later imposed relaxed constraints on the observed dictionary/coefficient pairs across image domains for improved performance. Wang et al. \cite{wang2012semi} further proposed a semi-coupled dictionary
learning (SCDL) scheme by advancing a linear mapping for cross-domain image sparse representation. Their method
has been successfully applied to applications of image SR and cross-style synthesis.

@@

\section{Double Semi-Couple Dictionary Learning}
In this section, we first formulate the real image denoising problem from the perspective of learning based model and then provide the optimization for the problem.
\subsection{Problem Formulation}
For real image denoising, we first collect clean natural images and real noisy images for training. Assume the $\mathbf{X}$ and $\mathbf{Y}$ are unpaired clean image patches and real noisy patches. Let the $\mathbf{X} = \mathbf{D}_{x}\mathbf{A}_{x}$ and $\mathbf{Y} = \mathbf{D}_{y}\mathbf{A}_{y}+\mathbf{V}_{y}$, where $\mathbf{V}_{y}$ is the real noise of which we don't know the distribution. 
\begin{equation}
\begin{split}
&\min_{\mathbf{D}_{x},\mathbf{D}_{y},\mathbf{A}_{x},\mathbf{A}_{y}}
\emph{E}_{data}(\mathbf{X},\mathbf{D}_{x},\mathbf{A}_{x})+
\emph{E}_{data}(\mathbf{Y},\mathbf{D}_{y},\mathbf{A}_{y},\mathbf{V}_{y})
\\
&
+\emph{E}_{map}(f_{1}(\mathbf{A}_{x}),f_{2}(\mathbf{A}_{y}))+
\emph{E}_{reg}(\mathbf{A}_{x},\mathbf{A}_{y},f_{1},f_{2},\mathbf{D}_{x},\mathbf{D}_{y},\mathbf{V}_{y})
\end{split}
\end{equation}

>>>>

\subsection{Our Contributions}
The contributions of this paper are summarized as follows:
\begin{itemize}
\item We propose a noval method which combine the external and internal PG prior for real noisy image denoising problem;
\item Our method doesn't need noise modeling and estimation, and the noise levels of real noisy images are automatically expresssed by the singular values of learned subspace;
\item We achieve much better performance, visual quality, PSNR, SSIM, and speed for real image denoising problem.

\end{itemize}

\section{Related Work}
\subsection{Patch Group Prior of Natural Images}
Patch prior is an approximation of the prior of natural images. There are several famous work on this area such as the K-SVD algorithm \cite{ksvd}. The seminar work on patch prior modeling is the expected patch log likelihood (EPLL), which models the space of natural image patches via Gaussian Mixture Model. Recently, the Patch Group prior \cite{pgpd} is proposed to directly model the non-local self similarity within natural images. The patch group prior demonstrate better properties via better image denoising performance on natural images. However, PGPD only utilizes the information of clean natural images, but not fully make full of the NSS information of noisy input images. In this paper, we combine the information of external natural clean images and internal real noisy images to achieve adaptive patch group prior modeling. In fact, we use the external Pacth Group prior to guide the structural clustering of internal patch groups in real noisy images. For each cluster of PGs, we propose to use PCA for subspace learning. The eigenvectors are the basis of this subspace and hence can be used as an orthonormal dictionary. The eigenvalues reflect the information describing the noise levels and hence can be used as parameters for image denoising. Noted that the dictionary and parameters are obtained via a fully unsupervised way by subspace learning. Therefore, our model is highly adaptive to the noisy input images.

@@

\section{Patch Group Prior Guided Internal Structural Clustering and Subspace Learning}
In this section, we first formulate the real image denoising problem from the perspective of learning based model and then provide the optimization for the problem.
\subsection{Problem Formulation}
For real image denoising, we first collect clean natural images and real noisy images for training. Assume the $\mathbf{X}$ and $\mathbf{Y}$ are unpaired clean image patches and real noisy patches. Let the $\mathbf{X} = \mathbf{D}_{x}\mathbf{A}_{x}$ and $\mathbf{Y} = \mathbf{D}_{y}\mathbf{A}_{y}+\mathbf{V}_{y}$, where $\mathbf{V}_{y}$ is the real noise of which we don't know the distribution. 
\begin{equation}
\begin{split}
&\min_{\mathbf{D}_{x},\mathbf{D}_{y},\mathbf{A}_{x},\mathbf{A}_{y}}
\emph{E}_{data}(\mathbf{X},\mathbf{D}_{x},\mathbf{A}_{x})+
\emph{E}_{data}(\mathbf{Y},\mathbf{D}_{y},\mathbf{A}_{y},\mathbf{V}_{y})
\\
&
+\emph{E}_{map}(f_{1}(\mathbf{A}_{x}),f_{2}(\mathbf{A}_{y}))+
\emph{E}_{reg}(\mathbf{A}_{x},\mathbf{A}_{y},f_{1},f_{2},\mathbf{D}_{x},\mathbf{D}_{y},\mathbf{V}_{y})
\end{split}
\end{equation}
